
\documentclass[11pt,a4paper,sans]{moderncv}    % Use the moderncv style
\usepackage{lmodern}
\moderncvstyle{classic}                        % Style options: banking, classic, casual
\moderncvcolor{blue}                           % Color options: blue, orange, green, etc.

% Personal data
\name{Jennifer}{Derkits}


\begin{document}

% Title
\makecvtitle

% Career Objective
\section{Career Objective}
To obtain a doctoral degree in Genomics and pursue a career in teaching and research.

% Education
\section{Education}
\cventry{2013}{Master of Science in Biology}{Virginia Commonwealth University}{Richmond, VA}{}{}
\cventry{1998}{Bachelor of Science in Biology, Minor in Psychology}{Longwood University}{Farmville, VA}{}{}
\cvitem{Thesis}{Genetic and Molecular Analysis of Canalization at the Maize \textit{r1} locus}

% Professional Experience - Research
\section{Professional Experience (Research)}
\cventry{2010--2013}{Research Assistant}{Virginia Commonwealth University}{Richmond, VA}{}{
\begin{itemize}
    \item Mentored undergraduates in laboratory techniques and coordinated an industry partnership.
    \item Developed a maize colorimetric scale for assessing phenotypic kernel color.
\end{itemize}}

\cventry{1999--2009}{Research and Development Scientist III}{Wyeth}{Richmond, VA}{}{
\begin{itemize}
    \item Authored standard operating procedures and maintained detailed records for patents and FDA audits.
    \item Managed junior scientists and developed/validated HPLC methods.
\end{itemize}}

% Teaching Experience
\section{Professional Experience (Teaching)}
\cventry{2013--Present}{Adjunct Instructor}{J. Sargeant Reynolds Community College}{Richmond, VA}{}{
\begin{itemize}
    \item Developed online curriculum and facilitated lab sessions.
    \item Emphasized research and the scientific method in teaching.
\end{itemize}}

% Skills
\section{Skills}
\cvitem{Research}{Analytical, Detail-Oriented, HPLC, Gel Electrophoresis, Bioinformatics}
\cvitem{Technology}{Microsoft Office, JMP, TurboChrom, TotalChrom, Empower}

% Professional Development
\section{Professional Development}
\cvitem{2015--2016}{Faculty Learning Community – Outcomes-based assessment development}
\cvitem{2014}{TOP Teaching Online Program, Certified Online Instructor}

% Publications & Presentations
\section{Presentations and Publications}
\cvitem{2014}{A comparison of traditional vs. “flipped” classroom in general biology}
\cvitem{2013}{Maize Genetics Conference: Canalization at the \textit{r1} locus in Maize}

% Awards & Scholarships
\section{Awards and Scholarships}
\cvitem{2011--2013}{Graduate Teaching Assistantship}
\cvitem{2012}{Waller-Hibbs Scholarship}

\end{document}
